Distributed Version Control Systems

### 2010-06-07 laarsample.tex
comentario sobre tortoise-git

Systems like SVN have mature tool support and various plugins, but popular DVCS are catching up.
For these tools most complete interface is the command line, but for the usual operations, 
there are various visual tools to operate with the repository.
Git, in particular, is based on Linux and originally didn't work work out of the box in Windows, 
but with Cygwin. 
Now there is a fork of Git that ports it to windows, but the linux heritage is 
shown and the installation includes a Bash shell. 
Git also includes a portable GUI written in Tk, invoked with command ``git gui'' 
but while it is simple and easy to use, it is very incomplete (for example, 
it doesn't include the ``pull'' operation, among others).

Mercurial is much more portable, but some tools are also incomplete, like hg-subversion (a tool 
to interoperate with svn). Git has git-svn which allows to push and pull from svn repositories, 
easing transitions.

>>>>

Systems like SVN have mature tool support and various plugins, but popular DVCS are catching up.
For these tools most complete interface is the command line, but for the usual operations, 
there are various visual tools to operate with the repository.
Git, in particular, is based on Linux and originally didn't work work out of the box in Windows, 
but with Cygwin. 
Now there is a fork of Git that ports it to windows, but the linux heritage is 
shown and the installation includes a Bash shell. 
Git also includes a portable GUI written in Tk, invoked with command ``git gui'' 
but while it is simple and easy to use, it is very incomplete (for example, 
it doesn't include the ``pull'' operation, among others).
There are many other third-party GUIs for Git, but none of them has all available operations, in those
cases, the command line is the only way to do them. One of the most complete GUIs is SmartGit, but 
requires to purchase a (rather inexpensive) licence for commercial usage. An alternative is Tortoise-Git,
which is a fork of Tortoise-SVN that shares the same look-and-feel, while supporting most of the 
Git operations.

Git has git-svn which allows to push and pull from svn repositories, 
easing transitions.
